\title {Accelerating Spike-by-Spike Neural Networks \added{on FPGA} with Hybrid Custom Floating-Point and Logarithmic Dot-Product Approximation \deleted{on FPGA}}

\author{
	\uppercase{Yarib Nevarez}\authorrefmark{1},	
	\uppercase{David Rotermund}\authorrefmark{2},
	\uppercase{Klaus R. Pawelzik}\authorrefmark{3},
	\uppercase{Alberto Garcia-Ortiz}\authorrefmark{4} \IEEEmembership{Member, IEEE},
}

\address[1]{Institute of Electrodynamics and Microelectronics, University of Bremen, Bremen 28359, Germany (e-mail: nevarez@item.uni-bremen.de)}

\address[2]{Institute for Theoretical Physics, University of Bremen, Bremen 28359, Germany (e-mail: davrot@neuro.uni-bremen.de)}

\address[3]{Institute for Theoretical Physics, University of Bremen, Bremen 28359, Germany (e-mail: pawelzik@neuro.uni-bremen.de)}

\address[4]{Institute of Electrodynamics and Microelectronics, University of Bremen, Bremen 28359, Germany (e-mail: agarcia@item.uni-bremen.de)}

\tfootnote{This work is funded by the Consejo Nacional de Ciencia
	y Tecnologia - CONACYT (the Mexican National Council for
	Science and Technology)}

\markboth
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

\corresp{Corresponding author: Yarib Nevarez (e-mail: nevarez@item.uni-bremen.de).}

\begin{abstract}
  Spiking neural networks (SNNs) represent a promising alternative to
  conventional neural networks. In particular, the so-called
  Spike-by-Spike (SbS) neural networks provide exceptional noise
  robustness and reduced complexity. However, deep SbS networks
  require a memory footprint and a computational cost unsuitable for
  embedded applications. To address this problem, this work exploits
  the intrinsic error resilience of neural networks to improve
  performance and to reduce hardware complexity. More precisely,
  we design a vector dot-product hardware unit based on approximate computing
  with \replaced{configurable quality}{quality configurable design}
  using hybrid custom floating-point and logarithmic number
  representation. This approach reduces computational latency, memory
  footprint, and power dissipation while preserving inference
  accuracy. To demonstrate our approach, we address a design
  exploration flow using high-level synthesis and a Xilinx SoC-FPGA.
  \replaced{The}{As a result, the} proposed design \replaced{reduces
    $20.5\times$ computational latency and $8\times$ weight memory
    footprint, with}{ achieves $20.5\times$ latency enhancement,
    $8\times$ weight memory footprint reduction, and} less than
  $0.5\%$ of accuracy degradation on \added{a} handwritten digit
  recognition task.
	
\end{abstract}

\begin{keywords}
Artificial intelligence, spiking neural networks, approximate computing, logarithmic, parameterisable floating-point, optimization, hardware accelerator, embedded systems, FPGA
\end{keywords}

\titlepgskip=-15pt

\maketitle
